\documentclass[letterpaper,10pt]{letter}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}

\begin{document}
% If you want headings on subsequent pages,
% remove the ``%'' on the next line:
% \pagestyle{headings}

\begin{letter}{}

\address{2515 13th St NW\\
         Apt. 510\\
         Washington, DC 20009}

\opening{To Whom it may Concern:}

I am submitting this letter to be considered for the position of Data Scientist.
I have over a decade of experience developing and implementing complex physics-based models of physical systems and organizing and analyzing the resulting data.
In the course of this work I have developed keen knowledge of uncertainty analysis and propagation, particularly how it applies to data produced by computer models.
I write maintainable code by applying the best practices of software development such as version control, issue tracking, liberal documentation, and continuous integration. 
I am fluent in Python, particularly the scientific stack of numpy, scipy, matplotlib, pandas, etc., and have experience with MATLAB and SQLite.


In addition to data science and scientific software development, I have formally and informally managed research teams working on projects on the cutting edge of semiconductor and energy research.
I routinely made substantive contributions to both the technical and strategic direction of these projects, oftentimes having to learn new physics and technology outside my field and under a deadline.


Finally, I am a clear and empathetic communicator. 
I have written several peer-reviewed scientific papers, delivered technical presentations to both expert communities and policy makers, delivered briefings on our group's work to the management of the Army Research Laboratory, and successfully pitched project proposals.
Additionally, I have taught scientific programming through Software Carpentry Foundation workshops and I am currently working with researchers at the National Institute of Standards and Technology (NIST) to develop and deliver a series of Software Carpentry workshops for the NIST community to improve their scientists' software development capabilities.


Please call me at (919) 413-0396 or email joshua.r.smith@gmail.com to schedule a time to talk about how I can help contribute to Deep Learning Analytics.


\signature{Joshua Ryan Smith}

\closing{Sincerely}

%enclosure listing
%\encl{}

\end{letter}
\end{document}
